\Title

### 2023-02-07 Grimaldi-etal-BiolCybernetics.tex
local changes laptop

Let us now define a procedure of animating of natural scene by virtual eye-movements similar to that which was used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. A specific mechanism to do so are called saccades which are rapide eye movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average $2$ each second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of % N-V-phi

@@

Now that our motion detection task is defined in visual space, we can extend the convolution-based detection model to a 3D convolution so that the resulting model would also benefit from spatial invariance. The use of spatio-temporal filters on an event stream has improved the performance of CNNs for an action recognition task in a model by~\citet{ghosh_spatiotemporal_2019} and here we will use a similar strategy, but focus on using an event-based representation.

>>>>

%Let us now define a procedure of animating of natural scene by virtual eye-movements similar to that which was used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. 
We want to test our model on a motion detection task on a binary stream of events. This type of signal, typically recorded by a Dynamic Vision Sensor (DVS), is a good representation of the information sent by the retinal ganglion cells through the optic nerve. With binary events, the visual system is able to capture the dynamics of a natural scene and perform various cognitive tasks in a fast and efficient fashion. To train and test our model, we need to define a dataset for which we control for motion direction and velocity. 
First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. A specific mechanism to do so are called saccades which are rapid eye movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average $2$ each second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of % N-V-phi

@@

\subsubsection{The general model}
\subsubsection{Applied on this detection task}
Now that our motion detection task is defined in visual space, we can define the model that will be trained to solve the task. The use of spatio-temporal filters on an event stream has improved the performance of CNNs for an action recognition task in a model by~\citet{ghosh_spatiotemporal_2019} and here we will use a similar strategy, but focus on using an event-based representation.
